---
title: "TractDataValidation"
author: "Eva Phillips"
date: "2023-12-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%",
  fig.height = 4.5,
  fig.width = 7                
)
# Setup
library(leaflet)
library(tidyverse)
library(dplyr)
library(gt)
library(gtsummary)
library(sf)
library(tidyr)
library(raster)
library(readxl)

```



```{r}
path = file.path("/Users", "evaphillips", "Library/CloudStorage/OneDrive-nyu.edu/right-to-counsel-capstone-data/01_Eviction/baseline_2000-2018", fsep="/")
setwd(path)

#read in a dataset
all_tracts <- read.csv("tract_proprietary_valid_2000_2018.csv")

all_tracts_sum <- all_tracts  %>%
  group_by(county, year, state) %>%
  summarise(filings = sum(filings, na.rm = TRUE), 
            avg_rt = mean(filing_rate, na.rm=TRUE)) 
```



```{r}
#NYC
nyc_tracts <- all_tracts %>% filter(county %in% c('Kings County', 'New York County', 'Queens County', 'Bronx County', 'Richmond County') & state == 'New York') %>% dplyr::select(-"state")

nyc_tracts_sum <- nyc_tracts %>%
  group_by(county, year) %>%
  summarise(filings = sum(filings, na.rm = TRUE), 
            avg_rt = mean(filing_rate, na.rm=TRUE)) 
nyc_tracts_sum

nyc_tracts_sum_all <- nyc_tracts %>%
  group_by(year) %>%
  summarise(filings = sum(filings, na.rm = TRUE), 
            avg_rt = mean(filing_rate, na.rm=TRUE)) 
nyc_tracts_sum_all



#NYS - NYC
ny_tracts <- all_tracts %>% filter(!county %in% c('Kings County', 'New York County', 'Queens County', 'Bronx County', 'Richmond County') & state == 'New York')

ny_tracts_sum <- nyc_tracts %>%
  group_by(year) %>%
  summarise(filings = sum(filings, na.rm = TRUE), 
            avg_rt = mean(filing_rate, na.rm=TRUE)) 
nyc_tracts_sum



```

```


```{r}

nyc_tracts %>% filter(year >=2010) %>%
  ggplot(aes(x = year,
             y = filings)) +
  geom_line(aes(color = county)) +
  labs(title = "Total Filings by Year")

nyc_tracts  %>% filter(year >=2010) %>%
  ggplot(aes(x = year,
             y = avg_rt)) +
  geom_line(aes(color = county)) +
  labs(title = "Avg Filing Rate by Year")
```


```{r}
maricopa_tracts <- all_tracts_sum %>% filter(county == 'San Diego County')

maricopa_tracts %>% 
  ggplot(aes(x = year,
             y = avg_rt)) +
  geom_line(aes(color = county)) +
  labs(title = "Total Filings by Year")


```


```